additional3D

### 2021-07-07 additional.Rmd
final decisions

@@

```{r determinism_area_X_ethnic_size, echo = FALSE}
lg <-  read.csv("lg_etlib.csv",sep=";")[,1]
etlb_bs <- read.csv("et_lib_fc_bothfalse.csv",sep=",",skip=6)
names(etlb_bs) <- lg
etlb_bs$ID <- "bsl"

etlb_mj <- read.csv("et_lib_fc_mj.csv",sep=",",skip=6)
names(etlb_mj) <- lg
etlb_mj$ID <- "mj_et"

etlb_mn <- read.csv("et_lib_fc_mn.csv",sep=",",skip=6)
names(etlb_mn) <- lg
etlb_mn$ID <- "mn_et"

etlb <- rbind(etlb_bs,etlb_mj,etlb_mn) %>% group_by(density,fraction_blue,circle_blue,circle_orange,et_mn_on,et_mj_on,dominant,ID) %>% summarise_all(mean) %>%  gather(key = subgroup, value = Segra, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or"), "Value" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")),"Ethnic"), 
 `ethnicity` = fct_relevel(fct_collapse(subgroup, "Majority" = c("de_sq_bl","dv_cl_bl","de_cl_bl","dv_sq_bl"), "Minority" = c("de_sq_or","de_cl_or","dv_sq_or","dv_cl_or")), "Majority"),
`orientation` = fct_relevel(fct_collapse(subgroup,"Conservatives" = c("de_sq_bl","dv_sq_bl","de_sq_or","dv_sq_or"), "Liberals" = c("de_cl_bl","dv_cl_bl","de_cl_or","dv_cl_or")), "Conservatives"), 
`type` = fct_relevel(fct_collapse(subgroup,"Conservative Majority" = c("de_sq_bl","dv_sq_bl"),
      "Liberals Majority" = c("de_cl_bl","dv_cl_bl"),
      "Conservative Minority" = c("de_sq_or","dv_sq_or"),
      "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Conservative Majority"))

etlb_df <- etlb %>% filter(fraction_blue == 50 | fraction_blue == 80)

lmn <- ggplot(etlb_df[which(etlb_df$type  == "Liberals Minority"),],aes(x=dominant,y=Segra,  linetype = as.factor(ID) ,color= as.factor(`segregation`))) + geom_point(shape="square") + geom_line() +
  facet_wrap(~ fraction_blue, scales = "free_y") +
  theme_bw()

cmj
cmn

lmj
lmn

pic_lm <- ggpubr::ggarrange(lmj,lmn, nrow = 2,  common.legend = T, legend = "bottom")

pic_cm
pic_lm

>>>>

```{r combine majority}

sens_vlmj1 <- read.csv("sens_vlmj.csv",skip=6,sep=",")
names(sens_vlmj1) <- read.csv("lg_full.csv",sep=";")[,1]

sens_vlmj2 <- read.csv("sens_vlmj2.csv",skip=6,sep=",")
names(sens_vlmj2) <- read.csv("lg_full.csv",sep=";")[,1]

sens_vlmj <- rbind(sens_vlmj1,sens_vlmj2)
sens_vlmj$ID <- "mj"

sens_vlmn <- read.csv("sens_vlmn.csv",skip = 6, sep= ",")
names(sens_vlmn) <- read.csv("lg_full.csv",sep=";")[,1]
sens_vlmn$ID <- "mn"

sens_vl <- rbind(sens_vlmj,sens_vlmn)

write.csv(sens_vl,"sens_vl.csv",row.names = F)

sens_vl <- read.csv("sens_vl.csv",sep =",") %>% select(-c(run)) %>%
  group_by(density,fraction_blue,circle_blue,circle_orange,eth_con_loc,eth_con_min,val_lib_loc,val_lib_min,eth_lib_loc,eth_lib_min,val_con_loc,val_con_min,ID) %>% summarise_all(mean) %>%  gather(key = subgroup, value = Segra, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or"), "Value" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")),"Ethnic"), 
 `ethnicity` = fct_relevel(fct_collapse(subgroup, "Majority" = c("de_sq_bl","dv_cl_bl","de_cl_bl","dv_sq_bl"), "Minority" = c("de_sq_or","de_cl_or","dv_sq_or","dv_cl_or")), "Majority"),
`orientation` = fct_relevel(fct_collapse(subgroup,"Conservatives" = c("de_sq_bl","dv_sq_bl","de_sq_or","dv_sq_or"), "Liberals" = c("de_cl_bl","dv_cl_bl","de_cl_or","dv_cl_or")), "Conservatives"), 
`type` = fct_relevel(fct_collapse(subgroup,"Conservative Majority" = c("de_sq_bl","dv_sq_bl"),
      "Liberals Majority" = c("de_cl_bl","dv_cl_bl"),
      "Conservative Minority" = c("de_sq_or","dv_sq_or"),
      "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Conservative Majority"))

mj <- sens_vl %>% filter(ID == "mj") %>% filter(type == "Liberals Majority" | type == "Liberals Minority") %>% ggplot(aes(x=val_lib_loc,y=Segra, color = segregation, linetype = as.factor(val_lib_min))) + geom_point() + geom_line() + 
  facet_wrap(~ type)

mj

@@

```{r determinism_area_X_ethnic_size, echo = FALSE}
# lg <-  read.csv("lg_etlib.csv",sep=";")[,1]
# 
# etlb_bs <- read.csv("et_lib_fc_bothfalse.csv",sep=",",skip=6)
# names(etlb_bs) <- lg
# etlb_bs$ID <- "bsl"
# 
# etlb_mj <- read.csv("et_lib_fc_mj.csv",sep=",",skip=6)
# names(etlb_mj) <- lg
# etlb_mj$ID <- "mj_et"
# 
# etlb_mn <- read.csv("et_lib_fc_mn.csv",sep=",",skip=6)
# names(etlb_mn) <- lg
# etlb_mn$ID <- "mn_et"
# 
# etlb_bs2 <- read.csv("et_lib_fc_bothfalse2.csv",sep=",",skip=6)
# names(etlb_bs2) <- lg
# etlb_bs2$ID <- "bsl"
# 
# etlb_mj2 <- read.csv("et_lib_fc_mj2.csv",sep=",",skip=6)
# names(etlb_mj2) <- lg
# etlb_mj2$ID <- "mj_et"
# 
# etlb_mn2 <- read.csv("et_lib_fc_mn2.csv",sep=",",skip=6)
# names(etlb_mn2) <- lg
# etlb_mn2$ID <- "mn_et"
# 
# etlb <- rbind(etlb_bs,etlb_mj,etlb_mn,etlb_bs2,etlb_mj2,etlb_mn2)
# 
# write.csv(etlb,"etlb.csv",row.names=F)

etlb <- read.csv("etlb.csv",sep=",") %>% select(-c(run)) %>%
  group_by(density,fraction_blue,circle_blue,circle_orange,et_mn_on,et_mj_on,dominant,ID) %>% summarise_all(mean) %>%  gather(key = subgroup, value = Segra, de_sq_bl,dv_sq_bl,de_cl_bl,dv_cl_bl,de_sq_or,dv_sq_or,de_cl_or,dv_cl_or)  %>% mutate(
`segregation` = fct_relevel(fct_collapse(subgroup,"Ethnic" = c("de_sq_bl","de_cl_bl","de_sq_or","de_cl_or"), "Value" = c("dv_sq_bl","dv_cl_bl","dv_sq_or","dv_cl_or")),"Ethnic"), 
 `ethnicity` = fct_relevel(fct_collapse(subgroup, "Majority" = c("de_sq_bl","dv_cl_bl","de_cl_bl","dv_sq_bl"), "Minority" = c("de_sq_or","de_cl_or","dv_sq_or","dv_cl_or")), "Majority"),
`orientation` = fct_relevel(fct_collapse(subgroup,"Conservatives" = c("de_sq_bl","dv_sq_bl","de_sq_or","dv_sq_or"), "Liberals" = c("de_cl_bl","dv_cl_bl","de_cl_or","dv_cl_or")), "Conservatives"), 
`type` = fct_relevel(fct_collapse(subgroup,"Conservative Majority" = c("de_sq_bl","dv_sq_bl"),
      "Liberals Majority" = c("de_cl_bl","dv_cl_bl"),
      "Conservative Minority" = c("de_sq_or","dv_sq_or"),
      "Liberals Minority" = c("de_cl_or","dv_cl_or")), "Conservative Majority")) %>% filter(fraction_blue == 50| fraction_blue == 80)

cl <- list(
as.data.frame(cbind(subset(etlb, type == "Conservative Majority" | type == "Conservative Minority"), s = "conservatives")),
as.data.frame(cbind(subset(etlb, type == "Liberals Majority" | type == "Liberals Minority"), s = "liberals"))
)

for (i in cl) {

  p <- ggplot(i, aes(dominant,y=Segra,color =`segregation`,linetype = as.factor(ID) )) +
    geom_point(size = 1.5, shape = if(i$s == "conservatives"){"square"}else{"circle"}) +
    geom_line() +
    facet_wrap(type ~ fraction_blue,  scales = "free", labeller = labeller(fraction_blue = c("50" = "50% Majority", "80" = "80% Majority"))) + 
    scale_color_manual(values = c("darkgreen","purple"), labels = c("Ethnic","Value"), guide_legend(title = "Segregation:")) +
        scale_linetype_manual(values = c("solid","longdash","dotted"), labels = c("Baseline","Lib Maj","Lib Min"), guide_legend(title = "Beta Ethnic:")) +
    ylab("Spatial Clustering") +
    xlab("ß dominant") +
    theme_bw() +
    theme(legend.position = "bottom")

  plot(p)

  nm <- paste0(as.name(i$s),".jpg")
  ggsave(nm,p,path = "images")

}
